---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# suso2stata

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of suso2stata is to translate enablement and validation conditions from Survey Solutions' dialect of C# into their nearest equivalent in Stata through intelligent string interpolation.

## Installation

Since suso2stata is not yet available on CRAN, it can be installed from GitHub as follows:

``` r
if (!require("pak")) install.packages("pak")
pak::pak("lsms-worldbank/suso2stata")
```

## Usage

Translate one expression element at a time:

```{r one_at_time}
# Translate SuSo's `InList`, method that contains values inside `()`...
my_suso_expr <- "M4_Q01c_Amt != 0 && M4_Q01.InList(1,4,6,7,96)"

# ... to Stata's `inlist`, function whose parameters are a variable and values
my_stata_expr <- suso2stata::replace_InList(my_suso_expr)

# before
my_suso_expr
# after
my_stata_expr
```

Translate all expression elements in a pipeline:

```{r in_pipeline}
# start with a complex SuSo expression that includes several
# several SuSo-specific syntactic elements
my_complex_suso_expr <- "IsAnswered(M22A_Q10_qty_A) && M22A_Q09_A.ContainsAny(1, 2, 4)"

my_complex_stata_expr <- my_complex_suso_expr |>
  # first, replace `IsAnswered` with `!mi()`
  suso2stata::replace_IsAnswered() |>
  # next, replace `&&` with `&`
  suso2stata::replace_and() |>
  # then, replace `ContainsAny` with its Stata equivalent
  suso2stata::replace_ContainsAny()

# before
my_complex_suso_expr
# after
my_complex_stata_expr
```
